---
output: github_document
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# argminCS
Welcome! Here we have source code to perform argmin hypothesis test.

## Overview
The goal of argminCS is to produce confidence set of argmin from iid samples with a valid type 1 control, while exhibiting desirable statistical power. In particular, the method 'softmin.LOO' is the main innovative component in our paper *Winners with Confidence: Argmin Inference over a High-Dimensional Discrete Candidate Set*. Several other methods are also implemented within the package to ease method comparison and simulations. 

## Citation
If you use the **argminCS** package for your research or any experiment, please cite our paper "Winners with Confidence: Argmin Inference over a
High-Dimensional Discrete Candidate Set". 

## Installation

You can install the development version of argminCS from this [GitHub](https://github.com/) webpage with:

``` r
# install.packages("devtools")
devtools::install_github("xu3cl4/argminCS")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(argminCS)
dimension <- 4
sample.size <- 200
p <- 20
mu <- (1:p)/p
cov <- diag(length(mu))
set.seed(108)
data <- MASS::mvrnorm(sample.size, mu, cov)

## to test if 'dimension' is likely to be argmin with (default) softmin.LOO
difference.matrix <- matrix(rep(data[, dimension], p-1), 
                            ncol = p-1, 
                            byrow = FALSE) - data[, -dimension]
argmin.HT(difference.matrix, method='SML')

## rather than perform a hypothesis testing for a specific dimension, 
## one can directly generate a discrete confidence set by 
CS.argmin(data, method='SML')
```

## Detailed Tutorial
Here is a detailed [tutorial](https://xu3cl4.github.io/argminCS/demo_CSargmin.html). 

Regarding other details of methods, we encourage users to install the package and check function documentation.

## Loss Matrices
There are two differentially private loss matrices provided in this package for reproducibility. You can access them via

```{r}
file_2023 <- system.file("extdata", "loss_matrix_2023_differentially_private.csv", package = "argminCS")
loss.2023 <- read.csv(file_2023)
head(loss.2023[,1:5])
dim(loss.2023)

file_2024 <- system.file("extdata", "loss_matrix_2024_differentially_private.csv", package = "argminCS")
loss.2024 <- read.csv(file_2024)
head(loss.2024[,1:5])
dim(loss.2024)
```

## Key References

---
nocite: '@*'
---
